---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Stefan Schmidt

## Exercise 1

Explain what you are visualizing here:

Ratio of female/male members  in the 115th congress.

Put your figure here:

```{r exercise1,echo=FALSE}
cel %>%
  filter(congress == 115) %>%
  mutate(Gender=recode(female, `1` = "Female", `0` = "Male")) %>% 
  ggplot(aes(x = Gender, fill=Gender)) +
  geom_bar() +
  labs(
    title = "Gender Balance in the 115th Congress",
    y = "Count") +
  scale_fill_manual(values = c(Female="orange", Male="gray")) +
  guides(fill = "none")
```

## Exercise 2

Explain what you are visualizing here:

Gender balance in congress between 1973 and 2017.

Put your figure here:

```{r exercise2, echo = FALSE}
cel %>%
  group_by(year) %>%
  summarise(Female=sum(female), Male=n() - sum(female)) %>%
  pivot_longer(cols = Female:Male,
               names_to = "Gender",
               values_to = "Count") %>%
  ggplot(aes(x = year,
             y = Count,
             color = Gender)) +
  geom_line() +
  scale_color_manual(values = c(Female="orange", Male="gray")) +
  labs(x = "Year",
       title = "Gender Balance in Congress",
       subtitle = "1973 - 2017") +
  theme_bw()
```

## Exercise 3

Explain what you are visualizing here:

How is the number of passed bills distributed and is there a difference in
gender? Visualized for 115th congress.

Put your figure here:

```{r exercise3,echo=FALSE}
cel %>%
  filter(congress == 115) %>%
  select("seniority", "all_pass", "female") %>% 
  mutate(Gender=recode(female, `1` = "Female", `0` = "Male")) %>% 
  ggplot(aes(x = all_pass, fill = Gender, alpha = .5)) +
    geom_density() +
    scale_fill_manual(values = c(Female="orange", Male="gray")) +
    labs(x = "Bills Passed",
         y = "Density",
         title = "Distribution of Bills Passed in the 115th Congress",
         subtitle = "by Gender") +
    guides(alpha = "none")
```

## Exercise 4

Explain what you are visualizing here:

Does the productivity of a congress member (bills passed) depend on his/her
seniority (year in congress) and is there a difference by gender?
Visualized for 115th congress, with labeled top performers (bills passed > 10).

Put your figure here:

```{r exercise4,echo=FALSE}
cel %>%
  filter(congress == 115) %>%
  select("seniority", "all_pass", "female", "thomas_name") %>% 
  mutate(Gender=recode(female, `1` = "Female", `0` = "Male")) %>% 
  ggplot(aes(x = seniority, y = all_pass, color = Gender)) +
    geom_jitter() +
    geom_text(aes(label=ifelse(all_pass > 10, thomas_name, ''),
              hjust=-0.2,
              vjust=-0.2)) +
    labs(x = "Seniority",
         y = "Bills Passed",
         title = "Members Seniority and Bills Passed in the 115th Congress",
         subtitle = "by Gender") +
    scale_color_manual(values = c(Female="orange", Male="gray")) +
    facet_wrap(~ Gender) +
  guides(color = "none")
```
