---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Stefan Schmidt

## Exercise 1

Explain what you are visualizing here:

Distribution of family income split up by race.

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE
cces$Race = recode(cces$race,
                  `1` = "White",
                  `2` = "Black",
                  `3` = "Hispanic",
                  `4` = "Asian",
                  `5` = "Native American",
                  `6` = "Mixed",
                  `7` = "Other",
                  `8` = "Middle Eastern")
ggplot(cces, aes(x = faminc_new)) +
  geom_density() + 
    labs(x = "Income Level",
       y = "Density",
       title = "Family Income and Race") +
  facet_wrap(~ Race)
```

## Exercise 2

Explain what you are visualizing here:

Put your figure here:

```{r exercise2, echo = FALSE}
ggplot(cces, aes(educ, faminc_new, color = Race)) +
  geom_jitter() +
  labs(x = "Education",
       y = "Income",
       title = "Education and Family Income") +
  facet_wrap( ~ Race)
```

## Exercise 3

Explain what you are visualizing here:

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE

```

## Exercise 4

Explain what you are visualizing here:

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

```


#### Remove before uploading ####
Your submission should include the following:

- Using ggplot, create 
OK  - a scatter plot,
OK  - a distribution figure (box plot, histogram, or density plot),
  - bar plot, and
  - line plot.
OK - Use colors and facetting in at least one of your figures.
- Add a text annotation to at least one of the your figures.
- Use a ggtheme for one of your figures.
- Make sure your figures have titles and appropriately labeled axes.

Upload a .html version of your R Markdown report as your submission.
#### Remove before uploading ####
