---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Stefan Schmidt



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1, echo = TRUE}
cces %>%
  mutate(ideology=recode(
    ideo5,
    `1` = "Very liberal",
    `2` = "Liberal",
    `3` = "Moderate",
    `4` = "Conservative",
    `5` = "Very conservative")) %>% 
  ggplot(aes(x = ideology, fill = ideology)) +
  geom_bar() +
  guides(fill = "none") +
  labs(title = "Respondent Ideology",
       x = "Count",
       y = "Ideology")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2, echo = TRUE}
cces %>%
  mutate(Ideology=recode(
    ideo5,
    `1` = "Very liberal",
    `2` = "Liberal",
    `3` = "Moderate",
    `4` = "Conservative",
    `5` = "Very conservative")) %>% 
  mutate(imp_religion=recode(
    pew_religimp,
    `1` = "Very imp.",
    `2` = "Somewhat imp.",
    `3` = "Not too imp.",
    `4` = "Not imp.")) %>% 
  ggplot(aes(x = imp_religion, fill = Ideology)) +
  geom_bar() +
  labs(title = "Importance of Religion by Ideology",
       x = "Importance of Religion",
       y = "Count")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3, echo = TRUE}
tibble(
  Name = c(rep("Amanda", 6), rep("Betty", 6), rep("Carol", 6)),
  Semester = rep(1:6, 3),
  Grade = runif(18, 80, 100)) %>% 
ggplot(aes(x = Semester, y = Grade, color = Name)) +
  geom_line() +
  guides(color = "none") +
  labs(title = "Student Grades by Semester") +
  facet_wrap(~ Name)

```
